---
title: "HW2"
author: "Qi Qi"
date: "9/14/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Exercise1 Approximation of distribution function of standard normal

### 1.1 Abstract
Monte Carlo methods have been used to approximate the distribution function of standard normal. Box plots of bias are also plotted. 


### 1.2 Method
The distribution function of $N(0,1)$ is

$$ \Phi(t)=\int_{-\infty}^t\frac{1}{\sqrt{2\pi}}e^{-y^2/2}dy$$

I compute the true values at $t\in\{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$.

To calculate the approximated values, I generate random samples with sample size $n\in\{10^2, 10^3, 10^4\}$ and evaluate the approximation at all values of $t$ by Monte Carlo method:

$$\hat{\Phi}(t)=\frac{1}{n}\sum_{i=1}^{n}I(X_i\leq t)$$



### 1.3 Comparison of true values and approximations
I use ```pnorm``` function to calculate the true values of distribution function at all the values of $t$ and then compute the approximations by Monte Carlo method described previously. Table 1 is generated and contains $t$, true values and approximations at different sample size n.
```{r echo=FALSE}
t=c(0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
true_value<- pnorm(t, 0, 1)
apprx1<- NA
apprx2<- NA
apprx3<- NA
# n=10^2
x=rnorm(100, 0, 1)
for (i in 1:length(t)){
  apprx1[i]<- sum(x<=t[i])/100
}

# n=10^3
x=rnorm(1000, 0, 1)
for (i in 1:length(t)){
  apprx2[i]<- sum(x<=t[i])/1000
}

# n=10^4
x=rnorm(10000, 0, 1)
for (i in 1:length(t)){
  apprx3[i]<- sum(x<=t[i])/10000
}

tab<- cbind(t, true_value, apprx1, apprx2, apprx3)
knitr::kable(tab, col.names = c("t", "True value", "Approx at n=10^2", "Approx at n=10^3", "Approx at n=10^4"), caption = "Comparison of true values and approximation")
```


## Exercise2 
```.Machine$double.xmax``` is the largest normalized floating-point number. Normally, it is 1.797693e+308.

``` .Machine$double.xmin```is the smallest non-zero normalized floating-point number. Normally, it is $2.225074e-308$.

```.Machine$double.eps``` is the smallest positive floating-point number x such that $1 + x != 1$. Normally, it is 2.220446e-16.

```.Machine$double.neg.eps``` is a small positive floating-point number x such that $1 - x != 1$. Normally, it is 1.110223e-16.
